### 2015-05-24 docs/report/intro.tex
fixes title and intro tex sections.

\section{Introduction}
In 1965 Gordon Moore proposed the popularly known ``Moore's law" \cite{moore65}, which predicts that the number of transitors in integrated circuits will double every two years.
As a consequence, programs that use a single processor/core will automatically become faster without the need to modify them with that purpose in mind.

@@

On a different note, one of the tendencies that is beginning to take off is the use of EcmaScript \cite{es-web} (also known as Javascript) to create applications, such as video games, that were previously only considered viable in a native environment. This has been possible thanks to components like asm.js \cite{asm-web} and WebGL \cite{webgl-web} together with the constant evolution of browsers and JavaScript runtime engines.
In this context, one of the plans of the commitee that develops the language is to provide an API to simplify the processing of data in parallel for version 7 (ES7) of the language, with the goal of keeping up with native applications. Initiatives such as ParallelJS \cite{par-js} and River trail \cite{rivertrail} or the possibility of taking advantage of SIMD instructions \cite{js-simd} (single instruction multiple data) are some of the options to implement this.

>>>>

\section{Introduction}
In 1965 Gordon Moore proposed the popularly known ``Moore's law" \cite{moore65}, which predicts that the number of transistors in integrated circuits will double every two years.
As a consequence, programs that use a single processor/core will automatically become faster without the need to modify them with that purpose in mind.

@@

On a different note, one of the tendencies that is beginning to take off is the use of EcmaScript \cite{es-web} (also known as Javascript) to create applications, such as video games, that were previously only considered viable in a native environment. This has been possible thanks to components like asm.js \cite{asm-web} and WebGL \cite{webgl-web} together with the constant evolution of browsers and JavaScript runtime engines.
In this context, one of the plans of the committee that develops the language is to provide an API to simplify the processing of data in parallel for version 7 (ES7) of the language, with the goal of keeping up with native applications. Initiatives such as ParallelJS \cite{par-js} and River trail \cite{rivertrail} or the possibility of taking advantage of SIMD instructions \cite{js-simd} (single instruction multiple data) are some of the options to implement this.
